---
title: "Publications"
output:
  distill::distill_article
---

An index of my publications can also be found on [**Google Scholar**](https://scholar.google.ca/citations?user=yQn-c5MAAAAJ&hl=en)

# Publications



**Pelgrim, M.H.**, Espinosa, J., & Buchsbaum, D. (2022) Head-Mounted Mobile Eye-tracking in the Domestic Dog: A New Method *Behavior Research Methods. *\
[**Online**](https://link.springer.com/article/10.3758/s13428-022-01907-3)|[PDF](https://mpelgrim.github.io/papers/EyeTracking_Methods.pdf)


**Pelgrim, M. H**. & Buchsbaum, D. (2022) Categorizing Dogs’ Real World Visual Statistics. *Proceedings of the 44th Annual Conference of the Cognitive Science Society. *\ 
  [**Online**](https://escholarship.org/uc/item/769022r9) |[PDF](https://mpelgrim.github.io/papers/Categorizing_Dog_Visual_Stats.pdf)

ManyDogs Project, Espinosa, J., Bray, E. E., Buchsbaum, D., Byosiere, S.  Byrne M, Freeman, M. S., Gnanadesikan, G. E.,  Guran, A., Horschler, D. J., Huber, L., Johnston, A. M., MacLean, E. L., **Pelgrim, M. H.**, Santos, L., Silver, Z. A., Stevens, J. R., Völter, C. J., & Zipperling L. (pre-registered report accepted in principle). ManyDogs 1: A multi-lab replication study of dogs’ pointing comprehension. *Animal Behavior and Cognition*\
    [**Online**](https://psyarxiv.com/f86jq/)

**Pelgrim, M. H**., Espinosa, J., Tecwyn, E.C., Marton, S. M., Johnston, A.M., Buchsbaum, D. (2021) What’s the point? Domestic Dogs’ understanding of the accuracy of human social informants. *Animal Cognition.*\ [**Online**](https://doi.org/10.1007/s10071-021-01493-5) |[PDF](https://mpelgrim.github.io/papers/Accurate.pdf)


# Unpublished Work

Espinosa, J., Corbit, L., McGinn, K., **Pelgrim, M. H.**, & Buchsbaum, D. (in prep). Domestic dogs‘ sensitivity to the temporal priority principle.

```{r echo=FALSE}
htmltools::p(
  "
  Disclaimer: The PDFs provided may be copyrighted by the journals/edited volumes
  in which they are published. Access to these articles is provided to facilitate
  timely distribution of scientific knowledge, and is therefore intended for your
  personal use only. No commercial use may be made of these articles, nor is mass
  production of these articles permitted.
  ",
  style = "font-size: 70%; font-style: italic"
)
```


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
