---
title: "Publications"
output:
  distill::distill_article
---

An index of my publications can also be found on [**Google Scholar**](https://scholar.google.ca/citations?user=yQn-c5MAAAAJ&hl=en)

# Publications

**Pelgrim, M. H.**, Sundara Raman, S., Serre, T., & Buchsbaum, D. (2025) Evaluating Dogs’ Real-World Visual Environment andAttention. *Cognitive Science*, 49 (6)\
[**Online**](https://onlinelibrary.wiley.com/share/author/4W5K2EKKVYV2B4A6HSIZ?target=10.1111/cogs.70080) | [PDF](https://mpelgrim.github.io/papers/EyeTracking_Walks.pdf) 

**Pelgrim, M. H.**, He, I.X., Lee, K., Pabari, F., Tellex, S., Nguyen, T., & Buchsbaum, D. (2024) Find it like a dog: Using Gesture to Improve Object Search. *Proceedings of the Annual Meeting of the Cognitive Science Society*, 46\
[**Online**](https://escholarship.org/uc/item/0nk6w9fd) | [PDF](https://mpelgrim.github.io/papers/Pelgrim_CogSci_24.pdf) 

**Pelgrim, M. H.**, Tidd, Z., Byrne, M, Johnston, A. M., Buchsbaum, D. (2024) Synchronous citizen science with dogs. *Animal Cognition*, 27(1): 46.\
[**Online**](https://doi.org/10.1007/s10071-024-01882-6) | [PDF](https://mpelgrim.github.io/papers/Synchronous_24.pdf)

ManyDogs Project, Espinosa, J., Stevens, J.R., Alberghina, D., Alway, H.E.E., Barela, J.D., Bogese, M., Bray, E.E., Buchsbaum, D. Byosiere, S.-E., Byrne, M., Cavalli, C. M., Chaudoir, L. M., Collins-Pisano, C., DeBoer, H.J., Douglas L.E.L.C., Dror, S., Dzik, M.V., Ferguson, B., Fisher, L., Fitzpatrick, H.C., Freeman, M.S., Frinton, S.N., Glover, M.K., Gnanadesikan, G.E., Goacher, J.E.P., Golańska, M., Guran, C.-N.A., Hare, E., Hare, B. Hickey, M., Horschler, D.J., Huber, L., Jim, H.-L., Johnston, A.M., Kaminski, J. Kelly, D.M., Kuhlmeier, V.A., Lassiter, L., Lazarowski, L., Leighton-Birch, J., MacLean, E.L., Maliszewska, K., Marra, V., Montgomery, L.I., Murray, M.S., Nelson, E.K., Ostojić, L., Palermo, S.G., Parks Russell, A.E., **Pelgrim, M.H.**, Pellowe, S.D., Reinholz, A., Rial, L.A., Richards, E.M., Ross, M.A., Rothkoff, L.G., Salomons, H., Sanger, J.K., Santos, L., Shirle, A.R., Shearer, S.J., Silver, Z.A., Silverman, J.M., Sommese, A., Srdoc, T., St. John-Mosse, H., Vega, A.C., Vékony, K., Völter, C.J., Walsh C.J., Worth, Y.A., Zipperling, L.M.I., Żołędziewska, B., & Zylberfuden, S.G. (2023). ManyDogs 1: A multi-lab replication study of dogs’ pointing comprehension. *Animal Behavior and Cognition*, 10(3), 232-28\
[**Stage 1 registered report**](https://doi.org/10.31234/osf.io/f86jq)| [**Online**](https://doi.org/10.26451/abc.10.03.03.2023)|[PDF](https://mpelgrim.github.io/papers/ManyDogs1.pdf)


**Pelgrim, M. H.**, Espinosa, J., & Buchsbaum, D. (2023). The Impact of Quality and Familiarity on Dogs’ Food Preferences. *Proceedings of the Annual Meeting of the Cognitive Science Society*, 45. \
[**Online**](https://escholarship.org/uc/item/9v26x7rt) | [PDF](https://mpelgrim.github.io/papers/Pelgrim_CogSci_23.pdf)


ManyDogs Project, Alberghina, D., Bray, E., Buchsbaum, D., Byosiere, S.-E., Espinosa, J., Gnanadesikan, G., Guran, C.-N.A., Hare, E., Horschler, D., Huber, L., Kuhlmeier, V.A., MacLean, E., **Pelgrim, M.H.**, Perez, B., Ravid-Schurr, D., Rothkoff, L., Sexton, C., Silver, Z., & Stevens, J.R. (2023). ManyDogs Project: A big team science approach to investigating canine behavior and cognition. *Comparative Cognition and Behavior Reviews*, 18, 59-77 \
[**Online**](https://doi.org/10.3819/CCBR.2023.180004) | [PDF](https://mpelgrim.github.io/papers/ManyDogs_Review.pdf)



**Pelgrim, M.H.**, Espinosa, J., & Buchsbaum, D. (2022) Head-Mounted Mobile Eye-tracking in the Domestic Dog: A New Method *Behavior Research Methods. *\
[**Online**](https://link.springer.com/article/10.3758/s13428-022-01907-3)|[PDF](https://mpelgrim.github.io/papers/EyeTracking_Methods.pdf)


**Pelgrim, M. H**. & Buchsbaum, D. (2022) Categorizing Dogs’ Real World Visual Statistics. *Proceedings of the 44th Annual Conference of the Cognitive Science Society. * \
  [**Online**](https://escholarship.org/uc/item/769022r9) |[PDF](https://mpelgrim.github.io/papers/Categorizing_Dog_Visual_Stats.pdf)


**Pelgrim, M. H**., Espinosa, J., Tecwyn, E.C., Marton, S. M., Johnston, A.M., Buchsbaum, D. (2021) What’s the point? Domestic Dogs’ understanding of the accuracy of human social informants. *Animal Cognition.* \
[**Online**](https://doi.org/10.1007/s10071-021-01493-5) |[PDF](https://mpelgrim.github.io/papers/Accurate.pdf)


# Unpublished Work

Gatesy-Davis, A., **Pelgrim M. H.**, Malle, B., & Buchsbaum, D. (in prep) Measuring trust across species.

Ross, M. A., **Pelgrim M. H.**, Malle, B., & Buchsbaum, D. (in prep) Human Judgements of Dog Intelligence.

Espinosa, J., Corbit, L., McGinn, K., **Pelgrim, M. H.**, & Buchsbaum, D. (in prep). Domestic dogs‘ sensitivity to the temporal priority principle.

```{r echo=FALSE}
htmltools::p(
  "
  Disclaimer: The PDFs provided may be copyrighted by the journals/edited volumes
  in which they are published. Access to these articles is provided to facilitate
  timely distribution of scientific knowledge, and is therefore intended for your
  personal use only. No commercial use may be made of these articles, nor is mass
  production of these articles permitted.
  ",
  style = "font-size: 70%; font-style: italic"
)
```


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
